Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-13 paper/ms.tex
update manuscript

%
% TODO:
% * Zhou or Quinn: what is the SpType? Add to abstract, tables, and
% text. G0V has been assumed.
% * remove all bf todo's
%

@@

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, photometry from El Sauce
  and ASTEP400, and spectroscopy from CHIRON, FEROS, and Veloce.  We
  find that TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC
  2602.  The star and planet are therefore $35^{+11}_{-5}$
  million years old.  The planet is warm ($P = 8.3\,{\rm d}$) and
  slightly smaller than Jupiter.  Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the transits are grazing with
  $b=0.93\pm0.01$ and $R_{\rm p} = 0.79 \pm 0.07 \,R_{\rm Jup}$.  From
  radial velocity monitoring, we limit the minimum mass to less than
  1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a cause for
  concern, as they are usually indicative of astrophysical false
  positive scenarios.  Our follow-up data show that such scenarios are
  highly unlikely.  Our combined multi-color photometry,
  high-resolution imaging, and radial velocities rule out hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios,
  though limited by speckle imaging, formally remain a 0.2\%
  possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further observations of its stellar obliquity,
  atmosphere, and mass should confirm its planetary nature beyond
  doubt, and could improve our understanding of how the physical and
  orbital properties of exoplanets change in time.
\end{abstract}

@@

A number of other processes are expected to shape young exoplanets.
Planets with gaseous envelopes are thought to shrink as they contract
and as their atmospheres undergo photoevaporation \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
relative importance of contraction and photoevaporation is set by the
planetary mass, as well as the radiation environment.  The
effectiveness of photoevaporation can be inferred from observations of
planetary winds in the metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

@@

The discoveries made by K2 through its surveys of Taurus, the Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work
\citep[{\it
e.g.},][]{Mann_K2_25_2016,obermeier_k2_2016,Mann_et_al_2017,vanderburg_zeitVII_2018,ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018,rizzuto_zeitVIII_2018,livingston_k2-264_2019}.
Observations with K2 convincingly showed that at least some close-in
planets must form within about 10 Myr
\citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
hints that young planets may in fact be qualtiatively different from
their field counterparts.  For instance, based on its observed mass,
radius, and UV environment, the 700$\,$Myr K2-100b is probably
actively losing its atmosphere, and should become a bare rocky planet
over the next few hundred Myr
\citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
planets in V1298~Tau (23$\,$Myr) are also likely to be actively
photoevaporating, and could represent a precursor to Kepler's compact
multiple systems \citep{david_four_2019,david_warm_2019}.

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f2a.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with gray crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Zoomed
    windows of individual transits.  Gray lines are the best-fit
    transit model, which includes a local quadratic trend in each
    window.  {\it Bottom}: Phase-folded TESS transit. Gray points are
    2-minute PDCSAP flux measurements with the local spot-induced
    variation removed.  Black points are binned to 6-minute intervals.
    The black error-bar shows the median uncertainty for the black
    points.  The gray line is the best-fit model to the combined TESS
    and ground-based data (Table~\ref{tab:posterior}). 
		\label{fig:tessphot}
	}
\end{figure*}

% \begin{figure*}[!t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=.85\textwidth]{f1.pdf}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{
%     {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
%     \texttt{PDCSAP} median-subtracted relative flux at 2-minute
%     sampling in units of parts-per-thousand ($\times 10^{-3}$).
%     Starspot-induced variability is the dominant signal; flares
%     are shown with gray crosses.  Dashed lines indicate the five
%     transits observed by TESS.  {\it Bottom}: Zoomed windows of
%     individual transits.  Gray lines are the best-fit transit model,
%     which includes a local quadratic trend in each window.
% 		\label{fig:rawzoom}
% 	}
% \end{figure*}

% \begin{figure}[!t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=.47\textwidth]{f2a.pdf}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{
%     {\bf Phase-folded TESS transit.} Gray points are 2-minute PDCSAP flux
%     measurements with the local spot-induced variation removed.  Black
%     points are binned to 6-minute intervals. The black error-bar shows
%     the median uncertainty for the black points.  The gray line is the
%     best-fit model to the combined TESS and ground-based data
%     (Table~\ref{tab:posterior}). 
% 		\label{fig:phasefold}
% 	}
% \end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.49\textwidth]{f2b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Ground-based follow-up photometry.} The data were acquired
		using the 0.36m at El Sauce and the 0.40m ASTEP400 at Dome C. Black points are
		binned to 10-minute intervals.  The gray line is the best-fit
		model to the combined TESS and ground-based data. Models show
		$2\sigma$ lower limits on the transit depths in the Cousins-R and
		Johnson-B bandpasses used to rule out specific false positive
		scenarios (see Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B were possible
sources of blended eclipsing binary signals.  Star B is resolved in
the 0.36m images; Star A is not.

@@

\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure
time of $25\,$s, readout and processed overhead of $25\,$s).
Except for 12 May, our observations were conducted under stable
weather conditions, with clear skies, temperatures of about
$-70^\circ$C, and wind speeds inferior to 5\,ms$^{-1}$. Due to their
poor quality, we exclude from the analysis all data collected on May
12. We found that the optimal calibrated light curves of \tn\
correspond to an 11 pixel (10\,arcsec) and 14 pixel (12\,arcsec)
radius aperture for observations carried out on June and May,
respectively.  The data are reported in Table~\ref{tab:phot}, and are
plotted in Figure~\ref{fig:groundphot}.

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.46\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. Star A ($\Delta
    T=4.7$, $2.3''$ west) is detected in the autocorrelation function,
    and is also a resolved Gaia source.  It is co-moving with \tn, and
    its parallax and on-sky position imply that it is physically
    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:}
    Radial velocity (RV) measurements, with best-fit instrument
    offsets and jitter terms included.  The expected scatter from
    starspots based on $v\sin i$ and the photometric modulation
    amplitude is of order 300m$\,$s$^{-1}$.  {\it Bottom:} RV
    measurements phased to the orbital ephemeris of \pn.  The planet
    is not detected.  The black line shows a circular Keplerian orbit
    representing the $3\sigma$ upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

While the above constraints rule out HEBs, certain configurations of
BEB systems ({\it e.g.}, a background G2V+K6V binary) can produce blue
eclipses while remaining undetected along the line of sight.  Such
scenarios are constrained by the lack of an observed secondary
eclipse, and therefore require either eccentric orbits to avoid
secondary eclipses, or else a background twin binary system at double
the orbital period.  The only way to definitively rule out such
scenarios is to prove that the loss of light is from the target star,
for instance by detecting the Rossiter-McLaughlin effect during a
transit, and confirming that the spectroscopic transit is consistent
with the photometric transit.

@@

The ``Gaia'' curve in Figure~\ref{fig:fpscenario} combines both
point-source detections from imaging, and sources that show an
astrometric excess.  The curve was interpolated from Figure~4 of
\citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
indicative that there are no obviously present astometric companions.
The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
1.38, which is consistent with stars of similar brightness and color
\citep[][Appendix A]{lindegren_gaiasoln_2018}.

% chi2AL is 526.88
% NgAL is 276
% so, well, reduced chi2 is ~2, which seems bad. but it might (in fact,
% probably is) be because of the color-dependent stuff in the Gaia PSF
% model. Most Rp=10 PTFO members had red chi2 of at least 2.
% Also, looking at Lindegren+2018 Fig A.1., sqrt(reduced chi2) ~= 1.4
% is expected.
%
% --> you could still create the same RUWE vs cluster membership
%  diagnostic plot, just to be sure.

@@

% 151 T<15.1 stars within 360 arcseconds
% 298 T<16.0 stars within 360 arcseconds
The constraints on false-positive scenarios summarized in
Figure~\ref{fig:fpscenario} rule out the possibilities that {\it i)}
the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
are caused by hierarchical blends, and {\it iii)} the eclipses are
caused by neighboring stars outside $\approx 2''$.  The only scenario
not formally ruled out is a background eclipsing binary.  A simple
(fallacious) argument on the a priori probability of background blends
follows from counting statistics.  The local density of $T<15.1$ stars
around \tn, found by counting from TIC8, is $3.7\times10^{-4} \,{\rm
arcsec}^{-2}$.  Therefore within the relevant $\approx0.3''$ radius
not excluded by the SOAR HRCam contrast curve, for a randomly selected
star we would expect $1.0\times10^{-4}$ potential $T<15.1$
contaminants, which appears small.

@@

%

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} The  planet-to-star size ratio
    corresponds to a planet size between $0.65\,R_{\rm Jup}$ and
    $0.91\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
    This plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

We fitted the available time-series photometry of \pn\ as follows.
For the PDCSAP light curve, we first eliminated points that had
quality flags corresponding to any of bits $\{3, 4, 6, 8, 11, 12\}$.
This excluded cadences affected by coarse spacecraft pointing,
reaction wheel desaturation events, manual flags, cosmic ray hits, and
straylight from the Earth or Moon being present.  Inspecting the data,
we also manually excluded the two flares shown in
Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows
of $\pm 7\,{\rm hr}$ centered on each transit.

Our joint model for the TESS and ground-based data was an
\citet{exoplanet:agol19} transit with physical and orbital parameters
shared across all transit windows, plus a local quadratic trend
allowed within each window.  Select parameters and priors are listed
in Table~\ref{tab:posterior}.  In brief, we fitted for the shared
stellar parameters ($\log g, R_\star, u_0, u_1$), and the shared
planetary parameters ($t_0, P, b, \log(R_{\rm p}/R_\star)$).  There
were also three free trend parameters for each of the twelve transits
to account for the rotational variability.  This yielded a total of 44
free parameters, of which 8 have physical relevance, and 36 are
nuisance parameters.  To keep the table at a manageable length, we
only report the physically relevant parameters and derived quantities.

@@

While alternative approaches are available for simultaneously fitting
space and ground based photometry (in addition to radial velocimetry),
we opted for this approach because {\it i)} the radial velocimetry on
its own did not show evidence for a planetary signal, {\it ii)} we
expected that this approach would provide the best measurement of the
planetary ephemeris, which is key for follow-up efforts, and {\it
iii)} the assumption of identical limb-darkening across all bandpasses
seemed justified by the level of precision in the ground-based data.
The assumption of a constant radius across all bandpasses was tested
by independently fitting each ground-based transit while letting the
planetary radius float (Section~\ref{subsec:colorphot}). The transit
depths did not significantly change between different bandpasses.

The posteriors from this procedure are given in
Table~\ref{tab:posterior}.  The transit is grazing.  In the absence of
a strong prior on the stellar density, the grazing geometry would
hinder our ability to infer the planet-to-star size ratio.  However,
our priors on the stellar parameters from the cluster isochrone fit
are strong enough that we can derive two-sided limits on the
planet-to-star size ratio.  The relevant posterior probabilities are
shown in Figure~\ref{fig:subsetcorner}.

% The available data for \tn\ put us in an odd position. The transit
% data provide a minimum size due to the grazing geometry; the radial
% velocity data provide a maximum mass ($\approx$1.20 $M_{\rm jup}$).
% We could combine the two with an empirically-calibrated planetary
% mass-radius relation to force a more restrictive upper bound on the
% planetary size \citep[{\it e.g.},][]{chen_probabilistic_2016}.  The
% result of such an exercise would tautologically be that the planet
% would be smaller than the largest known Jovian planets ($\approx
% 2R_{\rm Jup}$).  This would also imply that the impact parameter is
% slightly below unity.  The planet's size, in our eyes, would remain
% poorly constrained even if we were to do this exercise, so we opt to 
% fit the photometry and radial velocities separately, to ensure clarity
% about which datasets are providing which constraints.

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{gaudi_prospects_2007}
\begin{align}
  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 14\,{\rm m\,s}^{-1},
\end{align}
for
\begin{align}
  f_{\rm LD} &= 1 - c_1 ( 1 - \mu ) - c_2 (1 - \mu )^2,
\end{align}
where $\mu \approx (1 - b^2)^{1/2}$, and for calculation purposes we
assumed $b=0.95$ and used stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
challenging, for a 1.84$\,$hr transit of a $V=10.6$ star, a detection
could be achieved with modern spectrographs.  The next viable total
transit windows from Chile occur in January and February of 2021;
there are also a few visible per season from other southern locations.

@@

If the RM measurements prove that the planet
is real, a campaign to measure the mass timed to coincide with
TESS sectors 36 and 37 ({\it i.e.}, from late March to late May of
2021) would significantly ease the extraction of the planetary Doppler
signal.  The reason is that the radial velocities, activity
indicators, and photometry could then be modeled simultaneously, which
would greatly constrain a Gaussian process model for the
spot-induced RV signal.

>>>>

%
% TODO:
% * Zhou or Quinn: what is the SpType? Add to abstract, tables, and
% text. G0/F9V has been assumed.
% * remove all bf todo's
%

@@

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, photometry from El Sauce
  and ASTEP400, and spectroscopy from CHIRON, FEROS, and Veloce.  We
  find that TOI$\,$837 is a $T=9.9$ G0/F9 dwarf in the southern open
  cluster IC 2602.  The star and planet are therefore $35^{+11}_{-5}$
  million years old.  The planet is warm ($P = 8.3\,{\rm d}$) and
  slightly smaller than Jupiter.  Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the transits are grazing with
  $b=0.95\pm0.01$ and $R_{\rm p} = 0.80^{+0.04}_{-0.03} \,R_{\rm
  Jup}$.  From radial velocity monitoring, we limit the minimum mass
  to less than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a
  cause for concern, as they are usually indicative of astrophysical
  false positive scenarios.  Our follow-up data show that such
  scenarios are highly unlikely.  Our combined multi-color photometry,
  high-resolution imaging, and radial velocities rule out hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios,
  though limited by speckle imaging, formally remain a 0.2\%
  possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further observations of its stellar obliquity,
  atmosphere, and mass should confirm its planetary nature beyond
  doubt, and could improve our understanding of how the physical and
  orbital properties of exoplanets change in time.
\end{abstract}

@@

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo
photoevaporation \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
relative importance of contraction and photoevaporation is set by the
planetary mass, as well as the radiation environment.  The
effectiveness of photoevaporation can be inferred from observations of
planetary winds in the metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

@@

The discoveries made by K2 through its surveys of Taurus, the Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work
\citep[{\it
e.g.},][]{Mann_K2_25_2016,obermeier_k2_2016,Mann_et_al_2017,vanderburg_zeitVII_2018,ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018,rizzuto_zeitVIII_2018,livingston_k2-264_2019}.
Observations with K2 convincingly showed that at least some close-in
planets must form within about 10 Myr
\citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
hints that young planets in clusters may in fact be qualitatively different from
their field counterparts.  For instance, based on its observed mass,
radius, and UV environment, the 700$\,$Myr K2-100b is probably
actively losing its atmosphere, and should become a bare rocky planet
over the next few hundred Myr
\citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
planets in V1298~Tau (23$\,$Myr) are also likely to be actively
photoevaporating, and could represent a precursor to Kepler's compact
multiple systems \citep{david_four_2019,david_warm_2019}.

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f2a.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with gray crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Zoomed
    windows of individual transits.  Gray lines are the best-fit
    transit model, which includes a local quadratic trend in each
    window.  {\it Bottom}: Phase-folded TESS transit. Gray points are
    2-minute PDCSAP flux measurements with the local spot-induced
    variation removed.  Black points are binned to 6-minute intervals.
    The black error-bar shows the median uncertainty for the black
    points.  The gray line is the best-fit model to the TESS
    data. 
		\label{fig:tessphot}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.49\textwidth]{f2b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36m at El Sauce and the 0.40m ASTEP400 at Dome C.
    Black points are binned to 10-minute intervals.  The gray line is
    the best-fit model to the combined TESS and ground-based data.
    Red and blue lines show $2\sigma$ lower limits on the transit depths in the
    Cousins-R and Johnson-B bandpasses used to rule out specific false
    positive scenarios (see Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

\paragraph{Custom aperture analysis}
Based solely on the TESS data, both Star A and Star B were possible
sources of blended eclipsing binary signals.  The typical FWHM for
stars in the El Sauce observations was $\approx 2.3''$, with a
variance of $\approx 0.2''$.  Star B is resolved in the 0.36m images;
Star A is not.

@@

\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
of $25\,$s, readout and processed overhead of $25\,$s).  Except for 12
May, our observations were conducted under stable weather conditions,
with clear skies, temperatures of about $-70^\circ$C, and wind speeds
inferior to 5\,ms$^{-1}$. Due to their poor quality, we exclude from
the analysis all data collected on May 12. We found that the optimal
calibrated light curves of \tn\ correspond to an 11 pixel (10\,arcsec)
and 14 pixel (12\,arcsec) radius aperture for observations carried out
on June and May, respectively.  The data are reported in
Table~\ref{tab:phot}, and plotted in Figure~\ref{fig:groundphot}.

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.46\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Follow-up speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. Star A ($\Delta T=4.7$, $2.3''$
    west) is detected in the autocorrelation function, and is also a
    resolved Gaia source.  It is co-moving with \tn, and its parallax
    and on-sky position imply that it is physically separated from
    \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} Radial velocity
    (RV) measurements, with best-fit instrument offsets and jitter
    terms included.  The expected scatter from starspots based on
    $v\sin i$ and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The black
    line shows a circular Keplerian orbit representing the $3\sigma$
    upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

While the above constraints rule out HEBs, certain configurations of
BEB systems ({\it e.g.}, a background G0V+K3V binary) can produce blue
eclipses while remaining undetected along the line of sight.  Such
scenarios are constrained by the lack of an observed secondary
eclipse, and therefore require either eccentric orbits to avoid
secondary eclipses, or else a background twin binary system at double
the orbital period.  The only way to definitively rule out such
scenarios is to prove that the loss of light is from the target star,
for instance by detecting the Rossiter-McLaughlin effect during a
transit, and confirming that the spectroscopic transit is consistent
with the photometric transit.

@@

The ``Gaia'' curve in Figure~\ref{fig:fpscenario} combines both
point-source detections from imaging, and sources that show an
astrometric excess.  The curve was interpolated from Figure~4 of
\citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
indicative that there are no obviously present astrometric companions.
The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
1.38, which is consistent with stars of similar brightness and color
\citep[][Appendix A]{lindegren_gaiasoln_2018}.

@@

The constraints on false-positive scenarios summarized in
Figure~\ref{fig:fpscenario} rule out the possibilities that {\it i)}
the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
are caused by hierarchical blends, and {\it iii)} the eclipses are
caused by neighboring stars outside $\approx 2''$.  The only scenario
not formally ruled out is a background eclipsing binary.  A simple
(fallacious) argument on the a priori probability of background blends
follows from counting statistics.  The local density of $T<15.1$ stars
around \tn, found by counting from TIC8, is $3.7\times10^{-4} \,{\rm
arcsec}^{-2}$.  Therefore within the relevant $\approx0.3''$ radius
not excluded by the SOAR HRCam contrast curve, for a randomly selected
star we would expect $1.0\times10^{-4}$ potential $T<15.1$
contaminants, which appears small.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} The  planet-to-star size ratio
    corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
    $0.97\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
    This plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

We also fitted the available time-series photometry of \pn\ using two
different approaches.  To derive the most precise possible ephemeris,
we fitted the ground and space-based transits simultaneously.  To the
derive the physical parameters of the planet, we fitted the TESS data
alone, due to our better understanding of the underlying systematic
trends and the higher precision.

For the PDCSAP light curve, we first eliminated points that had
quality flags corresponding to any of bits $\{3, 4, 6, 8, 11, 12\}$.
This excluded cadences affected by coarse spacecraft pointing,
reaction wheel desaturation events, manual flags, cosmic ray hits, and
straylight from the Earth or Moon being present.  Inspecting the data,
we also manually excluded the two flares shown in
Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows
of $\pm 7\,{\rm hr}$ centered on each transit.

Our model for time-series photometry data was an
\citet{exoplanet:agol19} transit with physical and orbital parameters
shared across all transit windows, plus a local quadratic trend
allowed within each window.  Select parameters and priors are listed
in Table~\ref{tab:posterior}, for the TESS-only model.  In brief, we
fitted for the shared stellar parameters ($\log g, R_\star, u_0,
u_1$), and the shared planetary parameters ($t_0, P, b, \log(R_{\rm
p}/R_\star)$).  There were also three free trend parameters for each
transit window to account for the local rotational variability.  In
the TESS-only model this yielded 23 free parameters, of which 8 were
physically relevant and 15 were nuisance parameters.  In the combined
TESS and ground-based model, there were an additional 7 transits, and
therefore an additional 21 nuisance parameters for a total of 44 free
parameters.

@@

We opted for this approach rather than a joint fit of the photometry
and radial velocities because the RVs on their own did not show
evidence for a planetary signal.  Our preference for using only the
TESS data to derive the transit parameters was in our view justified
by the systematic uncertainties inherent to ground-based light curve
production, particularly in comparison star selection.  Our assumption
of a constant radius across all bandpasses was tested by independently
fitting each ground-based transit while letting the planetary radius
float (Section~\ref{subsec:colorphot}). The transit depths did not
significantly change between different bandpasses.

The posteriors from fitting the TESS data alone are given in
Table~\ref{tab:posterior}.  Both approaches show that the transit is
nearly grazing.   The relevant posterior probabilities are shown in
Figure~\ref{fig:subsetcorner}.  To be precise, some of the posterior
has $b < 1 - R_{\rm p}/R_\star$ and therefore formally is not grazing,
and some of the posterior formally is grazing. For short-hand
convenience, we refer to this as grazing.  From experimenting with the
fits, we found that in the absence of a strong prior on the stellar
density, the inherent degeneracy between the impact parameter and
planet-to-star size ratio would have been much stronger.  However, our
priors on the stellar parameters from the cluster isochrone fit are
strong enough that we can derive two-sided limits on the
planet-to-star size ratio.

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{gaudi_prospects_2007}
\begin{align}
  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 14\,{\rm m\,s}^{-1},
\end{align}
for
\begin{align}
  f_{\rm LD} &= 1 - c_1 ( 1 - \mu ) - c_2 (1 - \mu )^2,
\end{align}
where $\mu \approx (1 - b^2)^{1/2}$, and for calculation purposes we
assumed $b=0.95$ and used stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
could be achieved with modern spectrographs.  The next viable total
transit windows from Chile occur in January and February of 2021;
there are also a few visible per season from other southern locations.
The most precise available ephemeris, found from our joint fit of the
TESS and ground-based photometry, is as follows.
\begin{align}
  t_0\ [{\rm BJD_{TDB}}] &= 2458574.2725293 \pm 0.0005870 \\
  P\ [{\rm d}] &= 8.3248764 \pm 0.0000155 \\
  T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
\end{align}

@@

If the RM measurements prove that the validated planet is real, a
campaign to measure the mass timed to coincide with TESS sectors 36
and 37 ({\it i.e.}, from late March to late May of 2021) would
significantly ease the extraction of the planetary Doppler signal.
The reason is that the radial velocities, activity indicators, and
photometry could then be modeled simultaneously, which would greatly
constrain a Gaussian process model for the spot-induced RV signal.
